Collaborative Visual Analysis on the Web with RCloud

### 2015-03-31 interviews.tex

Raif's usage is typical:
\begin{quote}
I've been sharing my notebooks in order for other people to see what
I've done. It's very convenient for that purpose. [...] We haven't
been editing them together, but we've been just sharing, and I've been looking
at things that other people do. So there's no collaborative aspect of it, like
developing the code, but there's sharing aspects for other people to see and for
me to see other people's notebooks.
\end{quote}

@@

An extremely common but more problematic use of forking is to
change parameters. Raif: ``I've been forking other people's notebooks [because]
I want to run it on a different part of data, or I want to change some parts, I
don't want to see this column, I want a different column, things like that.''

Currently parameters can be added to the URL, but adding user interface elements
to do the same thing requires expertise. The tool-builders see a need for
facilities to make it easier. Taylor complains that a notebook might say ``
`This is a report of the volume of all of our feeds for this month', and someone
would want to look at it for the next month or the previous month, so they'd
fork it to change the month.''

Jyothi calls it ``web-enabling'' the notebook: users ``can always fork the
notebooks and make changes, but I feel that if the owner of the notebook
web-enables it, [...] it's easier to run. Instead of
forking it, if they can set options, it's probably more efficient, and also they
can [still] fork it if they want to.''

@@

Automatic source control is also a popular feature. Clint says, ``instead of
looking back and saying I've got a billion files here in this subdirectory and I
hope I've got them backed up, if they're on RCloud I know they are. [...] I
don't have to worry about it, if I drop my computer in the bathtub, everythings
gone, because I'm not great about uploading my own for versioning.''

Bart points out that the automatic versioning works well for dealing with the
minutiae of web development:
\begin{quote}
I like the fact that it has a built-in editor, so
if you need to fix a typo in a link, or an extra line break or any of this other
nonsense, you can just switch to the edit view, pull up your asset, type
something, it's automatically saved, committed, everything. You don't have to go
back to your source code, change it, commit it to the repo, pull the repo to
your distribution version. None of that's necessary. A lot of web development is
fixing stupid little bugs, and you can do that instantly without a lot of
overhead, which is nice.
\end{quote}

On the other hand, saving every change leads to many fine-grained
versions. Rick says that for this reason, the history feature is not all that
helpful: ``I don't need something that keeps track of every mistake I've made or
every direction I've tried.'' Tagging these versions with names wouldn't
necessarily help because ``namespaces are already crowded, so trying to remember
the names of notebooks is hard, much less the names of states within each
notebook.''

@@

\subsection{Integrated analysis}
Integrating an analysis language into a web development environment is something
the tool developers really appreciate.  The structure of Horace's visualization
notebook means
\begin{quote}
the other guys who want to do analytics on the data, they can first pull
the data, do the analytics on it, and then feed the viewer the data. So
[...] anyone from the stats group [...] can always insert something in
between. [...] They don't have to rewrite the GUI part and they know how to
get the data source. Once you get the data into RCloud, then you have a
dataframe to work with, and then they know how to produce another
dataframe.
\end{quote}

Integrating R also helps Jyothi's topic modeling tool, described in the last section.
\begin{quote}
Having an open session with R certainly helps too, because both of my
applications need to be doing something with the data, so having an open session
where I can run R commands or R functions without having to invoke an API or
send out a request and then wait for the request to come back to do the results,
that kind of seamless integration is extremely helpful in writing the
application.
\end{quote}

@@

But there are interface reasons as well. Rick describes a common workflow:
\begin{quote}
I have the discipline of having a file that describes what I'm doing, with the
commands that I'm using, so that I can go back and recreate it or pass it on to
someone else. So it's a little bit like having an RCloud notebook. It's not
necessarily executable but most of the commands that I've typed are in there.
\end{quote}

However, the web interface of RCloud doesn't work for him. ``It's nice to have
it saved, but there's this trade-off between it making it easier for me to
present something or to save something, and my ease of typing and
correcting and things in a plain old editor window.''

Kenny also works with text file and command line, rearranging a file so the
good code is at the top of the file. When he's done, all the the right is
code at the top, and often shares the work by pasting it into an RCloud
notebook.

@@

The interface takes some learning. Clint says:
\begin{quote}
It took me a couple of weeks of
looking at it to become comfortable because I saw the cells and it just threw me
for a total loop. I mean, it's a good idea because [...] I can run it all at
once if I want or I can break these into sections for either debugging or
staging purposes. I really like it now, but when I first saw it, [it was] very
confusing.
\end{quote}

@@

For some users, the cells getting saved feels incompatible with exploratory data
analysis. Rick notes that Markdown is a form of literate programming, and
``being literate about anything typically takes a lot of rewriting and going
back over things. [...] I just want to explore a few things and then I'll know
what I want to write.''

>>>>

%% Raif's usage is typical:
%% \begin{quote}
%% I've been sharing my notebooks in order for other people to see what
%% I've done. It's very convenient for that purpose. [...] We haven't
%% been editing them together, but we've been just sharing, and I've been looking
%% at things that other people do. So there's no collaborative aspect of it, like
%% developing the code, but there's sharing aspects for other people to see and for
%% me to see other people's notebooks.
%% \end{quote}

@@

An extremely common but more problematic use of forking is to change
parameters. Raif: ``I've been forking other people's notebooks [because] I
want to run it on a different part of data, or I want to change some parts,
I don't want to see this column, I want a different column, things like
that.''  Taylor complains that a notebook might say ```This is a report of
the volume of all of our feeds for this month', and someone would want to
look at it for the next month or the previous month, so they'd fork it to
change the month.''

Currently parameters can be added to the URL, but adding user interface
elements to do the same thing requires expertise. The tool-builders see a
need for facilities to make it easier. Jyothi calls it ``web-enabling'' the
notebook: users ``can always fork the notebooks and make changes, but I
feel that if the owner of the notebook web-enables it, [...] it's easier to
run. Instead of forking it, if they can set options, it's probably more
efficient, and also they can [still] fork it if they want to.''

@@

Automatic source control is also a popular feature. Clint says, ``instead of
looking back and saying I've got a billion files here in this subdirectory and I
hope I've got them backed up, if they're on RCloud I know they are.''

%%  [...] I
%% don't have to worry about it, if I drop my computer in the bathtub, everythings
%% gone, because I'm not great about uploading my own for versioning.''

Bart points out that the automatic versioning works well for dealing with the
minutiae of web development:
\begin{quote}
I like the fact that it has a built-in editor, so
if you need to fix a typo in a link, or an extra line break or any of this other
nonsense, you can just switch to the edit view, pull up your asset, type
something, it's automatically saved, committed, everything. You don't have to go
back to your source code, change it, commit it to the repo, pull the repo to
your distribution version. 
%% None of that's necessary. A lot of web development is
%% fixing stupid little bugs, and you can do that instantly without a lot of
%% overhead, which is nice.
\end{quote}

On the other hand, saving every change leads to many fine-grained
versions. Rick says that for this reason, the history feature is not all that
helpful: ``I don't need something that keeps track of every mistake I've made or
every direction I've tried.''
%% Tagging these versions with names wouldn't
%% necessarily help because ``namespaces are already crowded, so trying to remember
%% the names of notebooks is hard, much less the names of states within each
%% notebook.''

@@

\subsection{Integrated analysis}
Integrating an analysis language into a web development environment is something
the tool developers really appreciate.  The structure of Horace's visualization
notebook means
\begin{quote}
the other guys who want to do analytics on the data, they can first pull
the data, do the analytics on it, and then feed the viewer the data. So
[...] anyone from the stats group [...] can always insert something in
between. [...] Once you get the data into RCloud, then you have a
dataframe to work with, and then they know how to produce another
dataframe.
\end{quote}

Integrating R also helps Jyothi's topic modeling tool, described in the
last section: ``Having an open session where I can run R commands or R
functions without having to invoke an API or send out a request and then
wait for the request to come back [...] is extremely helpful in writing the
application.''

@@

%% But there are interface reasons as well. Rick describes a common workflow:
%% \begin{quote}
%% I have the discipline of having a file that describes what I'm doing, with the
%% commands that I'm using, so that I can go back and recreate it or pass it on to
%% someone else. So it's a little bit like having an RCloud notebook. It's not
%% necessarily executable but most of the commands that I've typed are in there.
%% \end{quote}

The web interface of RCloud doesn't work for Rick: ``It's nice to have
it saved, but there's this trade-off between it making it easier for me to
present something or to save something, and my ease of typing and
correcting and things in a plain old editor window.''

Kenny also works with text file and command line, rearranging a file so the
good code is at the top of the file. When he's done, all the the right is
code at the top. RCloud does not readily support this workflow, but Kenny
often shares the work by pasting it into an RCloud notebook when he's done.

@@

The interface takes some learning. Clint says at first,
\begin{quote}
%% It took me a couple of weeks of
%% looking at it to become comfortable because 
I saw the cells and it just threw me
for a total loop. I mean, it's a good idea because [...] I can run it all at
once if I want or I can break these into sections for either debugging or
staging purposes. I really like it now, but when I first saw it, [it was] very
confusing.
\end{quote}

@@

%% For some users, the cells getting saved feels incompatible with exploratory data
%% analysis. Rick notes that Markdown is a form of literate programming, and
%% ``being literate about anything typically takes a lot of rewriting and going
%% back over things. [...] I just want to explore a few things and then I'll know
%% what I want to write.''
